### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex

\begin{definition}
  We say that set $\eventSet$ together with strict partial order $\identOrd$
  form an identifier set if:
  \begin{itemize}
    \item there exist distinguished initial identifier $e_0 \in \eventSet$;
    \item there exist function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}

>>>>

\begin{definition}
  We say that set $\eventSet$ together with strict partial order $\identOrd$
  form an identifier set if:
  \begin{itemize}
    \item there exists a distinguished initial identifier $e_0 \in \eventSet$;
    \item there exists a function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}
